EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-31 05_examples.tex
AA: Version 2.0 Iterated full text but intro and conclusions. Added a lot of references. Fixed (almost) all comments. Updated figAHM.
taking a pause before attacking intro  + conclusions. 

Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

\begin{center}
\begin{minipage}[t]{0.49\linewidth}
\textbf{Fortran}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
program ed_hm_bethe
   USE EDIPACK
   USE SCIFOR
   implicit none
   integer                :: Le=1000
   real(8)                :: wmixing=0.5d0
   real(8)                :: D=1d0
   integer                :: Nb
   real(8),allocatable    :: Bath(:)
   complex(8),allocatable :: Hloc(:,:,:,:)
   real(8),allocatable    :: Ebands(:),Dbands(:)
   complex(8),allocatable :: Smats(:,:,:,:,:)
   complex(8),allocatable :: Delta(:,:,:,:,:)
   !...  
   !Read variables
   call ed_read_input('inputED.conf')
   !Solver-specific arays
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Initialize Bethe arrays
   allocate(Ebands(Le),Dbands(Le))
   !From SciFortran:
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,Wband)*de
   !Set local H
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
//...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;
//Read  variables    
char input[] = "inputED.conf"; 
read_input(input);      
//Dimensions
int64_t d[4] = {Nspin,Nspin,Norb,Norb};
int total_size = d[0] * d[1] * d[2] * d[3];
int total_size_n5 = total_size * Lmats;    
//Solver-specific arrays
vector<complex<double>> Hloc(total_size);
vector<complex<double>> Smats(total_size_n5);
vector<complex<double>> Delta(total_size_n5);
//...
//Initialize Bethe arrays
vector<double> Ebands, Dbands;
//Locally defined functions:
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,Wband,de);
//set local H
ed_set_Hloc_single_N4(Hloc.data(), d);
$\phantom{.}$
$\phantom{.}$
\end{lstlisting}
\end{minipage}
\end{center}

@@

\begin{center} 
\begin{minipage}[t]{0.49\linewidth}
\textbf{Fortran}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
   !Initialize solver
   Nb=ed_get_bath_dimension()
   allocate(bath(Nb))
   call ed_init_solver(bath)
$\phantom{.}$   
$\phantom{.}$   
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
// Initialize solver
int Nb;
vector<double> Bath(Nb);
Nb = get_bath_dimension_direct();
int64_t bath_dim[1] = {Nb};
init_solver_site(Bath.data(), bath_dim);
\end{lstlisting}
\end{minipage}
\end{center}

@@

\item[{\tiny {\it User}}] Update the Weiss field via the {\bf self-consistency}
  relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) +
    \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$ or, equivalently, $\Delta = \tfrac{D}{4}G_\mathrm{imp}$.

@@

\begin{center} 
\begin{minipage}[t]{0.49\linewidth}
\textbf{Fortran}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
!DMFT loop
do while(.not.converged.AND.iloop<nloop)
    iloop=iloop+1     
    !Call ED Solver
    call ed_solve(bath)     
    !Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
    call ed_get_sigma(Smats,'m')
    !Build local Green's function
    wfreq = pi/beta*(2*arange(1,Lmats)-1)
    do i=1,Lmats
       zeta= xi*wfreq(i)+xmu - Smats(1,1,1,1,i)
       Gmats(1,1,1,1,i)=sum(DOS/(zeta-Ene))*de  
    enddo

@@

    !Check convergence: from ${\color{comment-color}\mathrm{DMFTtools}}$
    converged=check_convergence(Delta,&
          dmft_error,Nsuccess,Nloop)

enddo
$\phantom{.}$   
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
//DMFT loop
while (iloop < Nloop && !converged) {
  //Call ED Solver
  solve_site(Bath.data(),bath_dim,1,1);      
  //Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
  get_sigma_site_n5(Smats.data(),//
      0,0,wm.data(),Lmats,0);
  //Build a local Green's function
  for (int i=0;i<Lmats;++i) {
    zeta= wm[i] + xmu - Smats[i];
    Gmats[i] = complex<double>(0.0,0.0);
    for (int j=0; j< Le; j++) {
      Gmats[i]+=Dbands[j]/(zeta-Ebands[j]);
    }
  }
  //Self-consistency
  for (int i = 0; i < Lmats; ++i) {
    Delta[i] = 0.25 * D * Gmats[i];
  }
  //Fit -> new bath
  chi2_fitgf_single_normal_n5(Delta.data(),//
      delta_dim,Bath.data(),bath_dim,1,0,1);
  //Check convergence: local functions
  converged = check_convergence(Delta,//
      dmft_error, Nsuccess, Nloop, comm);  
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\item[{\tiny {\it User}}] Update the Weiss field's components, respectively 
  $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
  relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_\mathrm{loc}(i\omega) +
  {\mathbf \Sigma}(i\omega)$ in Nambu space.

@@

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
    \caption{\label{figEx2}%
      \textbf{The BCS to BEC crossover.}
      (a) Evolution of the spectral functions
      $-\Im{G_\mathrm{loc}(\omega)}/\pi$ as a function of increasing
      attraction $U$. 
      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
      function of the attraction $U$. Data for BCS (gray) is compared
      to DMFT results (blue line and symbols). 
      (c) The correlation strength
      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
      attraction $U$ across the BCS-BEC crossover. 
      (d) Comparison of the double occupation $D=\langle n_\up
      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
      solid line) and DMFT (blue solid line and symbols). 
      (e) Superconducting order
      parameter $\phi$ as a function of temperature across the
      superconductor-to-normal phase transition. Data for $U=4$. The
      fit highlights the critical behavior with a mean-field exponent
      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_\mathrm{c}=0.61$.       
        }
\end{figure}

@@

The evolution of the order parameter with attraction $U$ is presented in panel (B). The figure  
highlights the crossover from the weak-coupling BCS regime to the 
strong-coupling BEC regime. In the BCS limit, $\phi$ displays the 
characteristic exponential growth with $U$, known to be 
computationally challenging. In the opposite, strong-coupling, limit 
$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the mean-field result 
(gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime.

To quantify these dynamical effects, we plot in panel (C) the 
{\it correlation strength}~\cite{Amaricci2015PRL,Amaricci2016PRB}
$\Theta=|S(i\omega\to 0)-S(i\omega\to\infty)|/S(i\omega\to\infty)$. 
Large values of $\Theta$ indicate an anomalous self-energy with 
significant dynamical effects, hence a more correlated superconducting state.
Our results show that the DMFT solution significantly departs from the MF picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D). We show the evolution of the double occupancy $d = \langle n_\up n_\dw \rangle$ as a function of $U$ compared to the MF expression $d = 1/4 + \phi^2$. The DMFT 
results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
the MF result.

@@

One of the features introduced in \NAME is the possibility of treating local phonons in conjunction with the superconductive phase,
i.e. \textbf{ed\_mode=superc}. 
In this example, we discuss  the normal and
superconductive solution of the pure Holstein model on the Bethe
lattice within DMFT.
We stress that, using Fortran API, the code
implementation for this specific case is essentially identical to the listing reported in the sections
\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
\ref{SecExamplesAHM} ({\tt ed\_mode=superc}).

So we consider the model introduced in \secu{SecExamplesBetheDMFT}
with $U=0$ and the additional phononic and electron-phonon terms:
\begin{equation} \label{eqex:H_Holstein}
    H_\mathrm{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
    b_i)\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i\sigma}
    -\frac{1}{2}\right)\Big]. 
\end{equation}
We consider the half-filling regime of the particle-hole symmetric Bethe lattice density of states. We set the half-bandwidth as our energy unit $D=1$ and introduced the electron-phonon coupling $\lambda = \tfrac{2g^2}{\omega_0D}$.  
The iterative DMFT solution algorithm follows the same principles
illustrated in the previous sections.

\paragraph{Results}
In the following we discuss the adiabatic ($\omega_0\to0$) to
anti-adiabatic ($\omega_0\to\infty$) crossover for
the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.

In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma\left(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}\right) \Big]^2,
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
choice of the coupling.

We characterize the model solution by showing the evolution of the
double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
the behavior for the normal solution ({\tt ed\_mode=normal}) against the superconductive
solution ({\tt ed\_mode=superc}). Our results capture the whole
crossover from adiabatic to anti-adiabatic regime. In the former
regime, the double occupation takes a similar value for the two
phases. However, approaching the anti-adiabatic regime, the two
solutions reach the limiting values corresponding to the residual
attraction \equ{HlikeAttraction}.   
To better characterize the nature of the superconducting
phase in the Holstein model, we report the evolution of the anomalous order
parameter $\phi$ in the adiabatic to anti-adiabatic crossover (panel (B) of \figu{figEx5}).
The DMFT results obtained with \NAME show a rapid increase in the
superconducting order parameter as phonon frequency grows
large. Finally, in the anti-adiabatic regime, $\phi$ saturates to a
finite value corresponding to the attractive Hubbard-like interaction
of strength $\lambda/2$.

@@

We proceed to demonstrate how to use the EDIpack2TRIQS compatibility
layer (\secu{sSecInteropTRIQS}) to solve a quantum system comprised by a
3-orbital correlated impurity coupled to a few non-interacting bath sites.
The interaction term of the impurity Hamiltonian is in the Hubbard-Kanamori
form (\equ{Hint}).

@@

One then proceeds to defining the system under consideration. In this case we
consider an impurity atom with three correlated orbitals and two bath states
per each impurity orbital. This information must be encoded in the fundamental
set objects that are later used to construct the solver.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=15, lastline=26]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The next step is to define a TRIQS many-body operator expression that represents
the Hamiltonian to be diagonalized.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=28, lastline=67]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
Finally, one creates a solver object and performs the actual calculation by
calling its method {\tt solve()}. This is normally the most time- and
memory-consuming step.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=69, lastline=83]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The computation results are readily available as attributes of the solver
object. The following code snippet shows how to access measured expectation
values of the static observables, and how to employ the plotting framework of
TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
functions (\figu{figEx3}).
\lstinputlisting[style=mypython,
                 mathescape=false,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=85, lastline=113]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}

\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
In this section we focus on the DMFT solution of the interacting
Bernevig-Hughes-Zhang (BHZ).
As shown in Ref.~\onlinecite{AmaricciPRB2022}, at moderate
interactions this model admits an excitonic phase in which opposite
orbital electrons and holes across the band gap bind into a coherent phase.

We consider a system of two-orbital electrons on a square
lattice interacting through a Hubbard-Kanamori term and describing
a quantum spin Hall insulator.
We consider a suitable matrix basis in terms of the Dirac
matrices $\Gamma_{a\a}=\sigma_a\otimes \tau_\a$, where $\sigma_a$ and
$\tau_\a$ are Pauli matrices, respectively, in the spin and orbital
pseudo-spin space. The  model Hamiltonian reads
$$
H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int},
$$
where $\psi_{k}=[c_{1\uparrow k}, c_{2\uparrow k},
c_{1\downarrow k}, c_{2\downarrow k} ]$ is the spinor collecting
annihilation operator $c_{a\sigma k}$ destroying an electron at
orbital $a=1,2$ with spin  $\sigma=\up,\dw$ and lattice momentum
$k$. The non-interacting part of the Hamiltonian is:
$$
H(k) = \left[M-2t(\cos{k_x}+\cos{k_y}) \right]\Gamma_{03} +
   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02},
$$
where $M$ is the mass term, which plays the role of a crystal
field splitting among the orbitals. The presence of this term breaks
the symmetry in the orbital pseudo-spin channel.
The  interaction reads: 
$$
   H_{\rm int} = (U-J)\frac{\hat{N}(\hat{N}-1)}{2} - J\left( \frac{1}{4}\hat{N}^2 +
   \hat{S_z}^2 - 2 \hat{T_z}^2\right),
 $$
 where $\hat{N}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{00}\psi_i$ is the
total density operator,
$\hat{S_z}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{30}\psi_i$ is the total
spin polarization operator and $\hat{T_z}=\tfrac{1}{2}\psi_i^\dagger
\Gamma_{03}\psi_i$ is the orbital pseudo-spin polarization operator.
This form corresponds to the density-density part of the
Kanamori interaction. We neglect the pair-hopping and spin-flip purely
for numerical reasons.

In the non-interacting regime, i.e. $U=J=0$ this model describes a
quantum spin Hall insulator (QSHI) for $M<4t$ and a trivial Band
Insulator (BI) for $M>4t$.
The transition point at $M=4t$ describes the formation of a gapless
Dirac state with linear band crossing at $k=[0,0]$.

>>>>

\begin{center}
\begin{minipage}[t]{0.49\linewidth}
\textbf{Fortran}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
program ed_hm_bethe
   USE EDIPACK
   USE SCIFOR
   implicit none
   integer                :: Le=1000
   real(8)                :: wmixing=0.5d0
   real(8)                :: D=1d0
   integer                :: Nb
   real(8),allocatable    :: Bath(:)
   complex(8),allocatable :: Hloc(:,:,:,:)
   real(8),allocatable    :: Ebands(:),Dbands(:)
   complex(8),allocatable :: Smats(:,:,:,:,:)
   complex(8),allocatable :: Delta(:,:,:,:,:)
   !...  
   !EDIpack: Read variables
   call ed_read_input('inputED.conf')

   !Solver-specific arrays. Using Rank-5  
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Construct Bethe DOS using SciFortran functions
   allocate(Ebands(Le),Dbands(Le))
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,Wband)*de
   !
   !EDIpack: Set impurity Hamiltonian
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
//...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;

//EDIpack: Read  variables    
char input[] = "inputED.conf"; 
read_input(input);      
//Dimensions
int64_t d[4] = {Nspin,Nspin,Norb,Norb};
int total_size = d[0] * d[1] * d[2] * d[3];
int total_size_n5 = total_size * Lmats;    
//Solver-specific arrays rank5
vector<complex<double>> Hloc(total_size);
vector<complex<double>> Smats(total_size_n5);
vector<complex<double>> Delta(total_size_n5);
//...
//Construct Bethe DOS
vector<double> Ebands, Dbands;

//Locally defined functions:
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,Wband,de);

//EDIpack: Set impurity Hamiltonian
ed_set_Hloc_single_N4(Hloc.data(), d);
\end{lstlisting}
\end{minipage}
\end{center}

@@

\begin{center} 
\begin{minipage}[t]{0.49\linewidth}
\textbf{Fortran}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
   !EDIpack: Initialize solver
   Nb=ed_get_bath_dimension()
   allocate(bath(Nb))
   call ed_init_solver(bath)
$\phantom{.}$   
$\phantom{.}$   
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
//EDIpack: Initialize solver
int Nb;
vector<double> Bath(Nb);
Nb = get_bath_dimension_direct();
int64_t bath_dim[1] = {Nb};
init_solver_site(Bath.data(), bath_dim);
\end{lstlisting}
\end{minipage}
\end{center}

@@

\item[{\tiny {\it User}}] Update the Weiss field via the {\bf self-consistency}
  relation: $\GG^{-1}_0(i\omega) = G^{-1}_\mathrm{loc}(i\omega) +
    \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
    $\Delta = \tfrac{D^2}{4}G_\mathrm{loc}$ or, equivalently, $\Delta = \tfrac{D^2}{4}G_\mathrm{imp}$.

@@

\begin{center} 
\begin{minipage}[t]{0.49\linewidth}
\textbf{Fortran}
\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
!DMFT loop
do while(.not.converged.AND.iloop<nloop)
    iloop=iloop+1

    !EDIpack: Call ED solver
    call ed_solve(bath)     
    !EDIpack: Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
    call ed_get_sigma(Smats,'m')

    !Build local Green's function
    wfreq = pi/beta*(2*arange(1,Lmats)-1)
    do i=1,Lmats
       zeta= xi*wfreq(i)+xmu - Smats(1,1,1,1,i)
       Gmats(1,1,1,1,i)=sum(DOS/(zeta-Ene))*de  
    enddo

@@

    !Check convergence: from ${\color{comment-color}\mathrm{DMFTtools}}$
    converged=check_convergence(Delta,&
          dmft_error,Nsuccess,Nloop)          
enddo
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
//DMFT loop
while (iloop < Nloop && !converged) {
  //EDIpack: Call ED solver
  solve_site(Bath.data(),bath_dim,1,1);      
  //EDIpack: Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
  get_sigma_site_n5(Smats.data(),//
      0,0,wm.data(),Lmats,0);
  //Build local Green's function
  for (int i=0;i<Lmats;++i) {
    zeta= wm[i] + xmu - Smats[i];
    Gmats[i] = complex<double>(0.0,0.0);
    for (int j=0; j< Le; j++) {
      Gmats[i]+=Dbands[j]/(zeta-Ebands[j]);
    }
  }
  //Self-consistency
  for (int i = 0; i < Lmats; ++i) {
    Delta[i] = 0.25 * D * Gmats[i];
  }
  //Fit -> new bath
  chi2_fitgf_single_normal_n5(Delta.data(),//
      delta_dim,Bath.data(),bath_dim,1,0,1);
  //Check convergence: local functions
  converged = check_convergence(Delta,//
      dmft_error, Nsuccess, Nloop, comm);  
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\item[{\tiny {\it User}}] Update the Weiss field's components, respectively 
  $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
  relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}^{-1}_\mathrm{loc}(i\omega) +
  {\mathbf \Sigma}(i\omega)$ in Nambu space.

@@

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
    \caption{\label{figEx2}%
      \textbf{The BCS to BEC crossover.}
      (a) Evolution of the spectral functions
      $-\Im{G_\mathrm{loc}(\omega)}/\pi$ as a function of increasing
      attraction $U$. 
      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
      function of the attraction $U$. Data for BCS (gray) is compared
      to DMFT results (blue line and symbols). Inset: the correlation strength
      $\Theta$ (see main text) as a function of the
      attraction $U$ across the BCS-BEC crossover. 
      (e) Superconducting order
      parameter $\phi$ as a function of temperature across the
      superconductor-to-normal phase transition. Data for $U=4$. The
      fit highlights the critical behavior with a mean-field exponent
      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_\mathrm{c}=0.61$.       
        }
\end{figure}

@@

The evolution of the order parameter with attraction $U$ is presented in panel (B). The figure  
highlights the crossover from the weak-coupling BCS regime to the 
strong-coupling BEC regime. In the BCS limit, $\phi$ displays the 
characteristic exponential growth with $U$, known to be 
computationally challenging. In the opposite, strong-coupling, limit 
$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the mean-field result 
(gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime. 
To further quantify these dynamical effects, we plot in the inset of the same panel the 
{\it correlation strength}~\cite{Amaricci2015PRL,Amaricci2016PRB}
$\Theta=|S(i\omega\to 0)-S(i\omega\to\infty)|/S(i\omega\to\infty)$. 
Large values of $\Theta$ indicate an anomalous self-energy with 
significant dynamical effects, hence a more correlated superconducting state.
Our results show that the DMFT solution significantly departs from the MF picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
% A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D). We show the evolution of the double occupancy $d = \langle n_\up n_\dw \rangle$ as a function of $U$ compared to the MF expression $d = 1/4 + \phi^2$. The DMFT 
% results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
% the MF result.

@@

One of the features introduced in \NAME is the possibility of treating local phonons in conjunction with the superconductive phase,
i.e. {\tt ed\_mode=superc}. In order to illustrate this property using a simple application, in this example we discuss the normal and
superconductive solution of the pure Holstein model on the Bethe lattice within DMFT.
We stress that  the code
implementation for this specific case is essentially identical to the listing reported in the sections
\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
\ref{SecExamplesAHM} ({\tt ed\_mode=superc}), provided electron-electron interaction is set to zero and phonon parameters are properly configured.

We consider the model introduced in \secu{SecExamplesBetheDMFT}
with $U=0$ and the additional phononic and electron-phonon terms:
\begin{equation} \label{eqex:H_Holstein}
    H_\mathrm{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
    b_i)\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i\sigma}
    -\frac{1}{2}\right)\Big]. 
\end{equation}
We focus on the half-filling regime of the particle-hole symmetric Bethe lattice DOS. We set the half-bandwidth as our energy unit $D=1$ and introduced the electron-phonon coupling $\lambda = \tfrac{2g^2}{\omega_0}$.  
The iterative DMFT solution algorithm follows the same principles illustrated in the previous sections.

\paragraph{Results.}
In the following we discuss the adiabatic ($\omega_0\to0$) to
anti-adiabatic ($\omega_0\to\infty$) crossover for
the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
%
In the anti-adiabatic limit, the Holstein interaction takes a
particularly simple form:
\begin{equation}\label{HlikeAttraction}
    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma\left(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}\right) \Big]^2,
\end{equation}
which describes a local Hubbard-like attraction among electrons
(mediated by local phonons).
In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
enters a Bipolaronic Insulating phase for our
choice of the coupling~\cite{Capone2006PRB}.

We characterize the model solution by showing the evolution of the
double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
the behavior for the normal  ({\tt ed\_mode=normal}) against the superconductive
solution ({\tt ed\_mode=superc}). Our results capture the whole
crossover from adiabatic to anti-adiabatic regime. In the former
regime, the double occupation takes a similar value for the two
phases. However, approaching the anti-adiabatic regime, the two
solutions reach the limiting values corresponding to the residual
attraction \equ{HlikeAttraction}.   
To better characterize the nature of the superconducting
phase in the Holstein model, we report the evolution of the anomalous order
parameter $\phi$ in the adiabatic to anti-adiabatic crossover, see panel (B) of \figu{figEx5}.
The DMFT results obtained with \NAME show a rapid increase in the
superconducting order parameter as phonon frequency grows
large. Finally, in the anti-adiabatic regime, $\phi$ saturates to a
finite value corresponding to the attractive Hubbard-like interaction
of strength $\lambda/2$.

@@

We proceed to demonstrate how to use the EDIpack2TRIQS compatibility
layer (\secu{sSecInteropTRIQS}) to solve a quantum system comprised by a
3-orbital correlated impurity coupled to a few non-interacting bath sites.
The interaction term of the impurity Hamiltonian is in the Hubbard-Kanamori
form of \equ{Hint}.

@@

One then proceeds to defining the system under consideration. In this case we
consider an impurity atom with three correlated orbitals and two bath states
per each impurity orbital, which corresponds to {\tt bath\_type=normal} in \NAME. This information must be encoded in the fundamental
set objects that are later used to construct the solver.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=15, lastline=26]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The next step is to define a TRIQS many-body operator expression that represents
the Hamiltonian to be diagonalized.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=28, lastline=67]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
Finally, one creates a solver object and performs the actual calculation by
calling its method {\tt solve()}. This is normally the most time- and
memory-consuming step.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=69, lastline=83]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The computation results are readily available as attributes of the solver
object. The following code snippet shows how to access measured expectation
values of the static observables, and how to employ the plotting framework of
TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
functions (\figu{figEx3}).
\lstinputlisting[style=mypython,
                 mathescape=false,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=85, lastline=113]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}

\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
In this section we focus on the DMFT solution of the interacting
Bernevig-Hughes-Zhang (BHZ).
As shown in Ref.~\cite{Amaricci2023PR}, at moderate
interactions this model admits an excitonic phase in which opposite
orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason,Amaricci2023PR,Giuli2023PRB}

We consider a system of two-orbital electrons on a square
lattice interacting through a Hubbard-Kanamori term and describing
a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Konig2007S,Hasan2010RMPa,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PR,Paoletti2024PR}.
We consider a suitable matrix basis in terms of the Dirac
matrices $\Gamma_{a\a}=\sigma_a\otimes \tau_\a$, where $\sigma_a$ and
$\tau_\a$ are Pauli matrices, respectively, in the spin and orbital
pseudo-spin space. The  model Hamiltonian reads
$$
H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int},
$$
where $\psi_{k}=[c_{1\uparrow k}, c_{2\uparrow k},
c_{1\downarrow k}, c_{2\downarrow k} ]^T$ is the spinor collecting
annihilation operator $c_{a\sigma k}$ destroying an electron at
orbital $a=1,2$ with spin  $\sigma=\up,\dw$ and lattice momentum
$k$. The non-interacting part of the Hamiltonian is:
$$
H(k) = \left[M-2t(\cos{k_x}+\cos{k_y}) \right]\Gamma_{03} +
   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02},
$$
where $M$ is the mass term, which plays the role of a crystal
field splitting among the orbitals. The presence of this term breaks
the symmetry in the orbital pseudo-spin channel.
The  interaction reads: 
$$
   H_{\rm int} = (U-J)\frac{\hat{N}(\hat{N}-1)}{2} - J\left( \frac{1}{4}\hat{N}^2 +
   \hat{S_z}^2 - 2 \hat{T_z}^2\right),
 $$
 where $\hat{N}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{00}\psi_i$ is the
total density operator,
$\hat{S_z}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{30}\psi_i$ is the total
spin polarization operator and $\hat{T_z}=\tfrac{1}{2}\psi_i^\dagger
\Gamma_{03}\psi_i$ is the orbital pseudo-spin polarization operator.
This form corresponds to the density-density part of the
Kanamori interaction. We neglect the pair-hopping and spin-flip purely
for numerical reasons \cite{Amaricci2022CPC}. 
%
In the non-interacting regime this model describes a
quantum spin Hall insulator (QSHI) for $M<4t$ and a trivial Band
Insulator (BI) for $M>4t$.
The transition point at $M=4t$ describes the formation of a gapless Dirac state at  $k=[0,0]$.
